%-------------------------
% Resume in Latex - Two Page Detailed Version
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for a two page layout (give it a bit more breathing room than 1 page)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\Large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{2pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Mohammed Jaseem Sabith} \\ \vspace{2pt}
    \large Forward Deployed Software Engineer $|$ Full Stack \& AI Solutions Expert \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:+971565798746}{+971-565798746} ~ \href{mailto:jaseemSabith@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{jaseemSabith@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/jaseem123/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jaseem123}} \\ \vspace{0pt}
    \href{https://github.com/Jaseem8}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    \href{https://jaseem8.github.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-4pt}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\vspace{-2pt}
\small{
    Senior Forward Deployed Software Engineer (\textbf{Tier 1 graduate}) with 7 years of expertise in deploying high-impact, \textbf{customer-centric} technical solutions. Expert in translating complex business requirements into \textbf{mission-critical} production systems, with a proven track record of \textbf{0-to-1 deployments} across fintech, AI, and public sectors. Passionate about solving high-stakes problems at the intersection of business strategy and core engineering.
}
\vspace{-6pt}

%-----------TECHNICAL SKILLS-----------
% RULE: Each bullet point entry in this section must have EXACTLY 162-164 visible characters in total (including spaces and the category name).
\section{Technical Skills \& Technologies}
\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{
    \begin{tabularx}{\linewidth}{@{}l X@{}}
      \textbf{Core Specialties}: & \textbf{System Architecture}, \textbf{Technical Solutions Design}, \textbf{Rapid Prototyping}, Full-Stack Optimization, API Design. \\ \vspace{2pt}
     \textbf{Frontend \& AI}: & React 18, Next.js, Redux, \textbf{Ant Design}, TypeScript, \textbf{Vite}, RAG, LangChain, LLMs, Vector Databases, Data Visualization. \\ \vspace{2pt}
     \textbf{Backend \& Cloud}: & NestJS, Node.js, Microservices, \textbf{AWS (S3, EC2, ECS, Lambda)}, \textbf{Cloud Reliability Engineering}, Docker, CI/CD Pipelines. \\ \vspace{2pt}
     \textbf{Databases}: & MongoDB, PostgreSQL, Amazon DynamoDB, MySQL, Firebase, Redis In-Memory, Relational and NoSQL DBs. \\ \vspace{2pt}
     \textbf{Tools \& Comms}: & Git, Agile/Scrum, \textbf{Technical Presentation}, Jira, New Relic, WebSockets, Postman API, Performance Profiling.
    \end{tabularx}
    }
 \end{itemize}
 \vspace{-6pt}

%-----------EXPERIENCE PAGE 1-----------
\section{Professional Experience}
\vspace{-2pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer - FullStack}{Dec 2024 -- Present}
      {\href{https://mycomera.com/}{Comera}}{Abu Dhabi, United Arab Emirates}
      \resumeItemListStart
        \resumeItem{\textbf{Mission-Critical Deployments:} Led the 0-to-1 deployment of complex technical solutions for high-stakes integrations including \textbf{Visa Principal Membership}, \textbf{TAMM (Abu Dhabi Govt)}, and \textbf{ADNOC} partnerships.}
        \resumeItem{\textbf{Solution Architecture:} Engineered high-performance analytics dashboards (\textbf{React 18}) and backend microservices (\textbf{NestJS}) tailored to executive-level requirements, accelerating decision-making speed by \textbf{3x}.}
        \resumeItem{\textbf{Performance Engineering:} Slashed system load and frontend latency by \textbf{35\%-40\%} by implementing advanced optimization patterns (\textbf{Vite}, aggressive code-splitting, and \textbf{Redis} write-through caching).}
        \resumeItem{\textbf{Scalable Integration:} Partnered with cross-functional teams to ensure the reliability and security of data-intensive platforms, sustaining \textbf{99.9\% uptime} for \textbf{900k+} users across diverse fintech environments.}
        \resumeItem{\textbf{High-Volume Data Pipelines:} Engineered fault-tolerant asynchronous payment and data pipelines using \textbf{Kafka} and \textbf{BullMQ}, reliably processing \textbf{50k+ daily transactions} with atomic consistency.}
        \resumeItem{\textbf{Full-Stack Observability:} Established a robust observability framework using \textbf{New Relic} and \textbf{Docker}, reducing mean-time-to-recovery (MTTR) by \textbf{60\%} and ensuring a flawless \textbf{99.9\% API uptime SLA} on \textbf{AWS}.}
        \resumeItem{\textbf{Enterprise Security:} Fortified application security by implementing robust \textbf{OAuth2/JWT} authentication flows and engineering sophisticated role-based access control (\textbf{RBAC}), ensuring 100\% compliance with institutional data privacy standards.}
        \resumeItem{\textbf{\href{https://jaseem8.github.io/\#comera}{Institutional Milestones:}} Part of the core engineering team during the launch of transformative fintech products featured in \textbf{WAM and Zawya}.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Web Developer}{Apr 2021 -- Nov 2024}
      {\href{https://www.chegg.com/}{Chegg}}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{\textbf{GenAI Product Innovation:} Instrumental in the engineering organization during the launch of \textbf{CheggMate (GPT-4)}, translating complex AI requirements into high-performing, stable frontend user experiences.}
        \resumeItem{\textbf{Frontend Performance Tuning:} Skyrocketed SEO and retention by migrating massive legacy systems from Webpack to \textbf{Vite}, leveraging aggressive code-splitting and optimization to slash bundle sizes by \textbf{35\%}.}
        \resumeItem{\textbf{Quality Assurance:} Established rigorous testing standards and mentored junior developers on \textbf{TypeScript} and accessibility, resulting in a \textbf{45\% reduction} in post-release critical frontend bugs.}
        \resumeItem{\textbf{\href{https://jaseem8.github.io/\#chegg}{Institutional Milestones:}} Supported engineering initiatives during the strategic \textbf{Scale AI partnership} and the \textbf{\$436M Busuu acquisition}.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Web Developer}{Jul 2019 -- Mar 2021}
      {\href{https://itjobxs.com/}{ITJOBXS}}{Remote}
      \resumeItemListStart
        \resumeItem{\textbf{0-to-1 Platform Development:} Directed the 0-to-1 greenfield development of a high-traffic recruitment platform (\textbf{React, Node.js}), drastically increasing candidate placements by architecting advanced filtering systems and a real-time notification engine from scratch.}
        \resumeItem{\textbf{Security \& Authentication:} Completely mitigated critical security vulnerabilities and ensured flawless \textbf{100\% compliance} with data privacy laws by implementing bulletproof authentication flows using \textbf{JWT, OAuth, and RBAC}.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-6pt}

%-----------PROJECTS-----------
\section{Key AI \& Technical Projects}
\vspace{-2pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Multi-Agent Research Assistant} $|$ \emph{LangGraph, LangChain, FAISS, Open-Source LLMs}}{}
          \resumeItemListStart
            \resumeItem{Developed an autonomous \textbf{Multi-Agent Research} system using \textbf{LangGraph}, capable of performing complex, multi-step tasks with fully cited sources.}
            \resumeItem{Implemented a \textbf{Self-Reflection Loop} and context-aware grading to ensure output quality, leveraging vector search for deep grounding.}
          \resumeItemListEnd
          \vspace{4pt}

      \resumeProjectHeading
          {\textbf{Domain-Specific RAG Chatbot} $|$ \emph{Pinecone, Hybrid Search, TypeScript}}{}
          \resumeItemListStart
            \resumeItem{Built an advanced \textbf{RAG} system using \textbf{Pinecone} and \textbf{Hybrid Search (BM25 + Semantic)} to accurately answer domain-specific queries from proprietary knowledge bases.}
            \resumeItem{Orchestrated open-source LLM integrations to reduce operational inference costs while maintaining sub-second latency for complex technical document retrieval.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-6pt}

%-----------EDUCATION-----------
\section{Education}
\vspace{-2pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute Of Technology (NIT)}{Calicut, Kerala}
      {Bachelor of Technology (B.Tech) - \textbf{7.55 CGPA}}{Aug 2015 -- May 2019}
      \resumeItemListStart
        \resumeItem{Achieved \textbf{\href{https://www.university.youth4work.com/nit_calicut_national-institute-of-technology-calicut/report/5}{Rank 6}} in \textbf{Top Students} institution-wide across all years and streams, demonstrating consistent academic excellence at a Tier-1 national institution.}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-6pt}

\end{document}
